Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-07-01 analysis/paper/paper.Rmd
Add years to table two, top 10 software used

```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
tab_s %>%
  flextable() %>%
  autofit() %>%
  set_caption("The top ten sofware programs that were found to be used in the papers that were surveyed.")
```

>>>>

```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
tab_t <- tabyl(rrpp_software, software_used, year)

tab_t <- tab_t[tab_t$software_used %in% tab_s$Software ,]

tab_t %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = T)) %>%
  arrange(desc(Total)) %>%
  rename(Software = software_used) %>% 
  flextable() %>%
  autofit() %>%
  set_caption(
    "The frequency of use of top ten sofware programs by year of publication that were found to be used in the papers that were surveyed."
  )
```
